R Notebook

### 2017-07-03 doc/RMD/wmn-differentiation.Rmd
Add questions related to host

# Summary

>>>>

# Host differentiation

There are three main hosts shared within the white mold nurseries:

| Cultivar | Susceptibility |
| ----- | ---- |
| Beryl | Susceptible |
| Bunsi | ? |
| G122  | Some Resistance |

These hosts are grown in the nurseries at different times and it is of interest
if cultivar can have an effect on population structure. Given the results of
Aldrich-Wolfe 2015, I would suspect that cultivar has no effect, but it's
important to verify this. We are going to use AMOVA and DAPC for this.

```{r host_AMOVA}
bebug <- dat11cc %>% 
  setPop(~Source) %>% 
  popsub("wmn") %>% 
  setPop(~Host) %>% 
  popsub(c("Beryl", "Bunsi", "G122"))
bebugd <- bruvo.dist(bebug, replen = other(bebug)$REPLEN)
(ssc_host_amova <- poppr.amova(bebug, ~Host, dist = bebugd, quiet = TRUE))
(ssc_host_amova <- poppr.amova(bebug, ~Host/Region, dist = bebugd, quiet = TRUE))
```

The AMOVA makes it clear that there's no differentiation between hosts. Let's
see what DAPC shows us.

```{r dapc, fig.width = 5, fig.height = 5.5}
bebug_dapc <- dapc(bebug, n.pca = 20, n.da = 2)
scatter(bebug_dapc, clabel = 0,
        legend = TRUE,
        scree.pca = TRUE, 
        scree.da = FALSE,
        col = viridis::plasma(3), 
        bg.inset = "grey90",
        bg = "grey90")

ggcompoplot::ggcompoplot(bebug_dapc, bebug, pal = viridis::plasma(3)) +
  theme(legend.position = "top")
```
